### 2017-07-13 architecture.tex
Minor edits

\subsection{Safe Collection}

@@

We extend our AWS-based Cloud Kotta services by leveraging additional
services and guarantees provided by AWS. 
Safe-collection policies are expressed on CLoud Kotta's S3-hosted data
%The data-store is implemented over S3 object store, and the
using Identity and Access Management(IAM) policies and S3 bucket policies.
A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

@@

@@

% implementation of access control
Access control on safe-collections for private datasets are managed by stewards. Access privileges to
safe-collections are granted, extended and revoked via S3 bucket policies. At the time of creation all
privileges over bucket policies are granted to the steward and revoked for all other entitites. This
guarantees that only the stewards can grant privileges on safe-collection. Access is granted by stewards
by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
access.

% cite garfinkel for de-identification risks

Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
are inspected and approved by a steward before export. This is enforced by setting the
\texttt{ExportStewardApprovalReqd} flag.
Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
results posted back to the same safe-collection, thus inheriting the same privileges as the source.
% worker roles are granted write privileges to the outputs section of a safe-collection
As a result, only stewards can view the results and export to a public safe-collection. Since results are
stored within the parent safe-collection, users can apply analysis operations on results without oversight,
and only request for export of the final results of a deep analysis pipeline.

>>>>

\subsection{Safe Collections}

@@

We extend our AWS-based \NAME services by leveraging additional
services and guarantees provided by AWS. 
Safe-collection policies are expressed on \NAMENS's S3-hosted data
%The data-store is implemented over S3 object store, and the
using Identity and Access Management(IAM) policies and S3 bucket policies.
A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

@@

\subsubsection{Policies}
Safe-collections are defined with policies that govern access to, and use of, 
data in that collection. The policies supported by safe-collections are as 
follows:

\textbf{SecurityClass:} A binary classification that enables or disables
the safe collection. Setting to \texttt{Public} means that the data is freely
accessible and no other policies can be set.  Setting to \texttt{Private}
requires that the subsequent policies are set.

\textbf{Classification:} Categorizes the type of data stored in the 
safe collection including specifying that the data is controlled by
a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).

\textbf{StewardGroup:} Defines the user(s) who are permitted to 
administer the safe collection. These users are subsequently 
allowed to modify policies and are tasked with managing the 
security of data within the collection.

\textbf{ReadAccess:} A set of policies that define who can
access data, under what conditions, and

@@

% implementation of access control
Access control on safe-collections for private datasets are managed by stewards. Access privileges to
safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
privileges over bucket policies are granted to the steward and revoked for all other entities. This
guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
access.

% cite garfinkel for de-identification risks
Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
are inspected and approved by a steward before export. This is enforced by setting the
\texttt{ExportStewardApprovalReqd} flag.
Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
results posted back to the same safe-collection, thus inheriting the same privileges as the source.
% worker roles are granted write privileges to the outputs section of a safe-collection
As a result, only stewards can view the results and export to a public safe-collection. Since results are
stored within the parent safe-collection, users can apply analysis operations on results without oversight,
and only request for export of the final results of a deep analysis pipeline.
